HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
weak attempt at a conclusion

These translation systems were used to translate texts derived from both NHS 24\footnote{\url{http://www.nhs24.com/}} and Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages. The first organisation is a public body providing healthcare and health-service related information in Scotland, whereas the second is an international NGO which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' which is part of the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.

@@

There are however a number of other serious consequences on focussing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\\
\item[Nominative argument structures,] which are completely ignored under HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

The paper concludes by outlining ongoing work to construct semi- and
fully-automatic variants of HUME.

>>>>

These translation systems were used to translate texts derived from both NHS 24\footnote{\url{http://www.nhs24.com/}} and Cochrane\footnote{\url{http://www.cochrane.org/}} into the four languages.
The first organisation is a public body providing healthcare and health-service related information in Scotland, whereas the second is an international NGO which 
provides independent systematic reviews on health-related research. From NHS 24, we selected the segments from their
``Health A-Z'' in the NHS Inform website, and the Cochrane texts come from their plain language summaries
and abstracts.

@@

There are however a number of other serious consequences on focussing on verbal
predicates. We conducted an analysis of the English UCCA Wikipedia
corpus, comprising
of 5324 sentences,
in order to assess the impact of the following problems: 
\\
\begin{inparadesc}
\item[Copula clauses] are treated in HMEANT simply as instances of the main verb ``be'', which
generally does not convey the meaning of these clauses. They appear in 21.7\% of the sentences,
according to conservative estimates that only considers non-auxilliary instances of ``be''.
\\
\item[Nominative argument structures,] which are ignored by  HMEANT are in fact highly
pervasive, appearing in 48.7\% of the sentences.
\\
\item[Linkers] expressing an inter-relation between
clauses (mainly discourse markers and coordinating conjunctions) appear in 56\% of the
sentences\footnote{Argument structures and linkers are explicitly marked in UCCA. We identified non-auxilliary instances of ``be'' and nouns using the NLTK standard tagger. Nominative argument structures are here defined as Scenes whose main relation is headed by a noun.}.
\end{inparadesc}

@@

We have introduced HUME, a human semantics based MT evaluation measure which addresses
a wide range of semantic phenomena. We have shown that it can be reliably annotated in 
several languages, and that annotation quality is robust to sentence length.
We believe that HUME and a future automated version of HUME will be able to guide the
development of a more semantically aware approach to MT.
